Finalised versions of normalisation and threshold

### 2020-07-30 simulations_MMPD6.Rmd
little changes in simulation

step1_data <- list(dat1, dat2)
response = "general_supply_kwh"
# global_harmony_iter1 <-  smart_meter10 %>%
#   global_threshold(harmony_tbl = harmonies,
#   response, step1_data = step1_data,
#    response, hierarchy_tbl = hierarchy_model)

>>>>

harmony_data <- list(dat1, dat2)
response = "general_supply_kwh"

global_harmony <- harmony_data %>%
  global_threshold(harmony_tbl = harmonies,
               response = "sim_dist",
               dist_distribution = "normal",
               dist_ordered = TRUE,
               create_gran_data = FALSE)

# global_harmony_iter1 <-  smart_meter10 %>%
#   global_threshold(harmony_tbl = harmonies,
#   response, step1_data = step1_data,
#    response, hierarchy_tbl = hierarchy_model)
